---
title: "Diamonds DataSet Analysis"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# GitHub Documents


```{r cars}
library(ggplot2)
```

### 1) Load the "diamonds" dataset contained in ggplot

```{r}
diamonds<-ggplot2::diamonds
```

### 2) Trace the number of diamonds according to their cut(diag in bars)

```{r}
ggplot(diamonds)+(mapping = aes(x=cut))+geom_bar() +ggtitle("Number of Diamonds based on Cut")
```

### 3) Make a histogram with carat in x and an interval of 0.5:
### How many diamonds are there between 0.25 and 0.75 carats?

```{r}
count<-ggplot(diamonds)+(mapping = aes(x=carat))+geom_histogram(binwidth = 0.5)+stat_bin(geom="text",aes(label=..count.., x=carat),binwidth = 0.5)+ggtitle("Histogram to count Diamonds based on Carats")
count
```

### To verify the number of diamonds

```{r}
ggplot_build(count) 
```

### There are 29498 diamonds 0.25 and 0.75 carats

### 4) Make a frequency polygon diagram (geom_freqpoly)

```{r}
ggplot(diamonds)+(mapping = aes(x=carat, color=cut))+geom_freqpoly()+ggtitle("Frequency polygon with each color corresponding to a different cut")
```

### 5) Same with bars filled with diamonds clarity 

```{r}
ggplot(diamonds)+(mapping = aes(x=carat, color=clarity))+geom_bar() +ggtitle("Bars filled with diamonds clarity ")
```

### 6) Draw several graphs to try to see which variable has the most influence on price 

```{r}
ggplot(diamonds)+(mapping = aes(x= carat, y=price))+geom_point(color="blue")+ggtitle("Price vs Carat")

ggplot(diamonds)+(mapping = aes(x= cut, y=price))+geom_point(color="blue")+ggtitle("Price vs Cut")


ggplot(diamonds)+(mapping = aes(x= clarity, y=price))+geom_point(color="blue")+ggtitle("Price vs Clarity")

ggplot(diamonds)+(mapping = aes(x= color, y=price))+geom_point(color="blue")+ggtitle("Price vs color")

ggplot(diamonds)+(mapping = aes(x= depth, y=price))+geom_point(color="blue")+ggtitle("Price vs depth")

ggplot(diamonds)+(mapping = aes(x= table, y=price))+geom_point(color="blue")+ggtitle("Price vs table")

ggplot(diamonds)+(mapping = aes(x= x, y=price))+geom_point(color="blue")+ggtitle("Price vs x")

ggplot(diamonds)+(mapping = aes(x= y, y=price))+geom_point(color="blue")+ggtitle("Price vs y")

ggplot(diamonds)+(mapping = aes(x= z, y=price))+geom_point(color="blue")+ggtitle("Price vs z")

```

## Based on the graphs above, I would conclude that the price of the diamonds directly depend on the Carat.